---
title: "F1 QA/QC Report"
author: "Contact:<a href = 'https://github.com/Breeding-Analytics/bioflow' target = '_blank'>Breeding Analytics Team, OneCGIAR</a> breedinganalytics@cgiar.org"
date: "`r format(Sys.time(), '%B %d, %Y')`"  
output: html_document
params:
  toDownload: FALSE
---

```{r setup, include=FALSE}

# knitr R markdown chunk options
knitr::opts_chunk$set(dependson = knitr::all_labels(),
                      echo = FALSE,
                      cache = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      comment = NA,
                      out.width = "100%",
                      error = TRUE)
options(knitr.kable.NA = '')

# loading necessary R packages ####
## data manipulation
library(dplyr)    # %>%, data cleaning functions
library(magrittr) # coerce col to factors or numeric

## outputs - graphs, tables
library(ggplot2)  # ggplot(), etc.
library(plotly)  # ggplot(), etc.
library(DT)       # datatable()
library(knitr)    # kable
library(grafify)
library(data.table)
library(shiny)
library(bslib)
library(adegenet)
```

```{r printfxn, include=FALSE}

# functions ####
# for printing tables (data.frames) - DT::datatable()
printTable <- function(DT, pageLength = 7, 
                         numericColNames = NULL, numRound = 3, 
                         scrollXOpt = FALSE, colNames = NULL, autoWidthOpt = FALSE,...) {
    
    DT <- data.frame(lapply(X = DT, 
                            FUN = function(x) {
                              if(is.numeric(x)){
                                round(x, numRound)
                              } else {
                                x
                              }
                            }))
    
    table <- DT::datatable(data = DT, 
                           colnames = colNames,
                           filter = "top", 
                           options = list(autoWidth = autoWidthOpt,
                                          dom = 'l<<t>pB>', 
                                          buttons = c('copy', 'csv', 'excel', 'print'),
                                          pageLength = pageLength,
                                          searchHighlight = TRUE,
                                          lengthMenu = c(7, 14, 21, 28, 35),
                                          scrollX = scrollXOpt),
                           extensions = 'Buttons',
                           rownames = FALSE,
                           ...)
    if (length(numericColNames) > 0){
      table <- table %>% DT::formatRound(columns = numericColNames,
                                     digits = numRound)
    }
    
    table
  }
```

```{r }

suppressWarnings(tryCatch({
  if(file.exists("./outputs/result.RData")){
    load("./outputs/resultQaPheno.RData")
  }else{
    load("resultQaPheno.RData")
  }
}, error = function(e) {
  shinyjs::hide()
}))

```
### Inputs and outputs of the F1 (QA/QC) module:


1. INPUT: Genotypic information of F1 individuals and Parents 

2. INPUT: Pedigree information connecting each F1 individual to two parents 

3. INPUT: Genotype QA/QC results 

3. OUTPUT: Probability that the F1 individual matches the genotype of the parents (matchProb)

4. OUTPUT: Expected heterozygosity in the progeny (HeteroMexp) 

5. OUTPUT: Observed heterozygosity in the progeny (HeteroMp) 

6. OUTPUT: Heterozygosity deviation (Expected - Observed) in the progeny (heteroDeviation)

7. OUTPUT: Number of highly informative markers for each cross (nScore2)

8. OUTPUT: Total number of markers used in the analysis for each cross (nMarkers)

9. OUTPUT: Average score of markers used in the analysis for each cross (AvgScore)

10. OUTPUT: Status of F1 invididuals (GOOD, QUESTIONABLE, BAD, PARENT FAIL, NO GENO DATA)

This qa/qc module allows users to identify which F1 individuals should be considered a TRUE F1 (GOOD), which ones should be investigated further (QUESTIONABLE) and which ones are not TRUE F1s (BAD). 

This dashboard also helps users to identify problems in the input data with flags to identify PARENT FAIL due to lack of pedigree information (HasPed), due to one of the parents not passing the heterozygosity threshold (parHetFilter) or due to one of the parents having no genotypic information (ParentHasGeno).

Additionally, ungenotyped F1 indviduals are also flagged (HasGeno / NO GENO DATA).

#### Parental uncertainty

The **parental_uncertainty** column indicates the confidence level in the parental genotypes used for F1 verification. During genotype loading, when multiple samples map to the same parental designation, the Individual Management module resolves them by computing pairwise IBS (Identity By State). Parents where all samples were identical (IBS = 1) are auto-resolved with high confidence. However, when samples disagree and the user manually selects a consensus, that parent is flagged as "uncertain" because the true parental genotype could not be unambiguously determined from the available data. The categories are:

- **No uncertainty**: Both parents were either auto-resolved (all samples identical) or had a single unambiguous genotype.
- **1 uncertain parent**: One parent of the cross was resolved by manual consensus from disagreeing samples.
- **2 uncertain parents**: Both parents were resolved by manual consensus.

F1 QA/QC results involving uncertain parents should be interpreted with caution, as Mendelian consistency checks depend on the correctness of the parental genotypes.

### Verification results
<p>&nbsp;</p>

The following plot and table show the values associated for the individuals on different metrics such as probability of matching the expected genotype, heterozygosity, among others and their classification according to the thresholds chosen in the input tabs

```{r }

if (is.null(result)){
  # invisible(NULL)
} else {
  predictions <- result$predictions
  idQa <- result$status[which(result$status$module %in% c("gVerif")),"analysisId"];
  idQa <- idQa[length(idQa)]
  predictions <- predictions[which( predictions$analysisId == idQa),]
  traitsTable <- unique(predictions$trait)
  traitsTable <- traitsTable[traitsTable != "parentalUncertainty"]
  
  
  if("params" %in% ls()){ # we will download the document
    shinyjs::hide()
  }else{
    tagList(
      shiny::selectInput(ns("traitQa"), 
                         label = "Verification measure:", 
                         choices = traitsTable,
                         selected = if ("probMatch" %in% traitsTable) "probMatch" else traitsTable[1]
      ),
      shiny::checkboxGroupInput(ns("filterUncertaintyPlot"),
                                label = "Filter by parental uncertainty:",
                                choices = c("No uncertainty", "1 uncertain parent", "2 uncertain parents"),
                                selected = c("No uncertainty", "1 uncertain parent", "2 uncertain parents"),
                                inline = TRUE
      )
    )
  }
  
}

```

```{r}
if (is.null(result)){
  # invisible(NULL)
} else {
  
  predictionsX <- result$predictions[which( result$predictions$analysisId == idQa),]
  modeling <- result$modeling[which(result$modeling$analysisId == idQa),]
  upperThres <- modeling[modeling$parameter == "UpperMatchProbThres","value"]
  #midThres <- modeling[modeling$parameter == "MidMatchProbThres","value"]
  lowerThres <- modeling[modeling$parameter == "LowerMatchProbThres","value"]
  
  upperThres = as.numeric(upperThres)
  #midThres = as.numeric(midThres)
  lowerThres = as.numeric(lowerThres)
  
  idx <- (predictionsX$trait == "probMatch") 
  
  status <- ifelse(predictionsX$predictedValue[idx] >= upperThres, "GOOD",
            #ifelse(predictionsX$predictedValue[idx] >= midThres, "LIKELY F1",
            ifelse(predictionsX$predictedValue[idx] >= lowerThres, "QUESTIONABLE","BAD"))
  
  prob_status <- unique(data.frame(designation = predictionsX$designation[idx],
                                   .status = status,
                                   stringsAsFactors = FALSE))
  
  # Override status for F1s whose parents failed the heterozygosity filter
  idx_het <- (predictionsX$trait == "parHetFilter")
  het_fail_desig <- predictionsX$designation[idx_het][predictionsX$predictedValue[idx_het] == 0]
  prob_status$.status[prob_status$designation %in% het_fail_desig] <- "PARENT FAIL"
  
  na_status = prob_status[is.na(prob_status$.status),]
  
  idx2 <- (predictionsX$designation %in% na_status$designation) & 
    (predictionsX$trait == "parHetFilter") 
  idx3 <- (predictionsX$designation %in% na_status$designation) & 
    (predictionsX$trait == "ParentHasGeno")
  idx4 <- (predictionsX$designation %in% na_status$designation) & 
    (predictionsX$trait == "HasPed")
  idx5 <- (predictionsX$designation %in% na_status$designation) & 
    (predictionsX$trait == "HasGeno")
  
  other_status <- ifelse(predictionsX$predictedValue[idx5] == 0, "NO GENO DATA",
            ifelse(predictionsX$predictedValue[idx2] == 0, "PARENT FAIL",
            ifelse(predictionsX$predictedValue[idx3] == 0, "PARENT FAIL",
            ifelse(predictionsX$predictedValue[idx4] == 0, "PARENT FAIL",NA))))
  
  prob_status[is.na(prob_status$.status),".status"] = other_status
  
  # Final catch-all: any remaining NA status gets NO GENO DATA
  prob_status$.status[is.na(prob_status$.status)] <- "NO GENO DATA"
  
  if("params" %in% ls()){ # we will download the document
    
       panels <- lapply(traitsTable, function(tr) {
                  predictions2 <- predictionsX[predictionsX$trait == tr, , drop = FALSE]
                  predictions2$..ord <- seq_len(nrow(predictions2))
                  predictions2 <- merge(predictions2, prob_status, by = "designation",
                                         all.x = TRUE, sort = FALSE)
                  predictions2 <- predictions2[order(predictions2$..ord), ]
                  predictions2$..ord <- NULL

        p <- ggplot2::ggplot(
          predictions2,
          ggplot2::aes(
          x = designation, y = predictedValue, fill = .status,
          text = paste0("Genotype: ", designation,
                    "<br>Value: ", round(predictedValue, 3),
                    "<br>Status: ", .status)
                      )
          ) +
          ggplot2::geom_col() +
          ggplot2::scale_fill_manual(
                                     name = "Match status",
                                    values = c(
                                               "NO GENO DATA" = "#f3b0b0",
                                               "BAD"     = "#f3b0b0",
                                               "PARENT FAIL"  = "#f3b0b0",
                                               "UNCERTAIN"    = "#FFD166",
                                               "QUESTIONABLE"    = "#C0CA33",
                                               "GOOD"         = "#A4D65E"
                                               )
                                    ) +
          ggplot2::labs(x = "Genotype", y = tr) +
          ggplot2::theme_classic() +
          ggplot2::theme(axis.text.x = ggplot2::element_blank())

          bslib::nav_panel(tr, plotly::ggplotly(p, tooltip = "text"))
      })

      # Create a pill-style tabset and RETURN it as the last expression
      do.call(bslib::navset_pill, panels)

    }else{ # regular rendering

      # Build parental uncertainty map for filtering
      unc_rows_plot <- predictionsX[predictionsX$trait == "parentalUncertainty", , drop = FALSE]
      if (nrow(unc_rows_plot) > 0) {
        unc_labels_plot <- c("No uncertainty", "1 uncertain parent", "2 uncertain parents")
        unc_map_plot <- data.frame(
          designation = unc_rows_plot$designation,
          parental_uncertainty = unc_labels_plot[as.integer(unc_rows_plot$predictedValue) + 1],
          stringsAsFactors = FALSE
        )
      } else {
        unc_map_plot <- data.frame(
          designation = unique(predictionsX$designation),
          parental_uncertainty = "No uncertainty",
          stringsAsFactors = FALSE
        )
      }

      plotly::renderPlotly({
        predictions2 <- predictionsX[which(predictionsX$trait == input$traitQa),]
        predictions2$..ord <- seq_len(nrow(predictions2))
        predictions2 <- merge(predictions2, prob_status, by = "designation",
                      all.x = TRUE, sort = FALSE)
        predictions2 <- predictions2[order(predictions2$..ord), ]
        predictions2$..ord <- NULL

        # Apply parental uncertainty filter to plot
        sel_unc <- input$filterUncertaintyPlot
        if (!is.null(sel_unc) && length(sel_unc) > 0 && length(sel_unc) < 3) {
          allowed_desig <- unc_map_plot$designation[unc_map_plot$parental_uncertainty %in% sel_unc]
          predictions2 <- predictions2[predictions2$designation %in% allowed_desig, , drop = FALSE]
        }
        # If nothing selected, show empty plot
        if (is.null(sel_unc) || length(sel_unc) == 0) {
          predictions2 <- predictions2[0, , drop = FALSE]
        }

        p <- ggplot2::ggplot(predictions2,
                           ggplot2::aes(x = designation, y = predictedValue, fill = .status,
                                        text = paste0("Genotype: ", designation,
                                                      "<br>Value: ", round(predictedValue, 3),
                                                      "<br>Status: ", .status))) +
        ggplot2::geom_col() +
        ggplot2::scale_fill_manual(name   = "Match status",
                                   values = c('NO GENO DATA' = "#f3b0b0",
                                              'BAD' = "#f3b0b0", 
                                              'PARENT FAIL' = "#f3b0b0",
                                              'UNCERTAIN' = "#FFD166", 
                                              'QUESTIONABLE'= "#C0CA33",
                                              'GOOD' = "#A4D65E")) +
        ggplot2::labs(x = "Genotype", y = input$traitQa) +
        ggplot2::theme_classic() +
        ggplot2::theme(axis.text.x = ggplot2::element_blank())
        fig <-  plotly::ggplotly(p)#, height = get_h()*2);
        fig
    })
  }
  
}

```


```{r}
if (is.null(result)){
  # invisible(NULL)
} else {
  predictions_wide <- reshape(predictionsX,
                              direction = "wide",
                              idvar    = c("designation","mother","father"),
                              timevar  = "trait",
                              v.names  = "predictedValue")
  
  OutputCols <- c("designation","mother","father","status","parental_uncertainty","probMatch","heteroMexp","heteroMp","heteroDeviation","avgScore","nScore2","nMarkers","HasGeno","HasPed","parHetFilter","ParentHasGeno")
  numericalColumns <- c("probMatch","heteroMexp","heteroMp","heteroDeviation","avgScore","nScore2","nMarkers")
  
  predictions_wide <- predictions_wide[,c(which(colnames(predictions_wide)%in%c("designation","mother","father") ), grep("predictedValue",colnames(predictions_wide)))]
  
  colnames(predictions_wide) = gsub("predictedValue.","",colnames(predictions_wide))
  
  predictions_wide <- merge(predictions_wide, prob_status, by = "designation",
                      all.x = TRUE, sort = FALSE)
  
  colnames(predictions_wide)[colnames(predictions_wide)==".status"]="status"

  # Add parental uncertainty column from predictions
  unc_rows <- predictionsX[predictionsX$trait == "parentalUncertainty", , drop = FALSE]
  if (nrow(unc_rows) > 0) {
    unc_labels <- c("No uncertainty", "1 uncertain parent", "2 uncertain parents")
    unc_map <- data.frame(
      designation = unc_rows$designation,
      parental_uncertainty = unc_labels[as.integer(unc_rows$predictedValue) + 1],
      stringsAsFactors = FALSE
    )
    predictions_wide <- merge(predictions_wide, unc_map, by = "designation", all.x = TRUE)
    predictions_wide$parental_uncertainty[is.na(predictions_wide$parental_uncertainty)] <- "No uncertainty"
  } else {
    predictions_wide$parental_uncertainty <- "No uncertainty"
  }

  predictions_wide = predictions_wide[,intersect(OutputCols, colnames(predictions_wide))]
  
  ped <- result$data$pedigree
  metaPed <- result$metadata$pedigree
  colnames(ped) <- cgiarBase::replaceValues(colnames(ped), Search = metaPed$value, Replace = metaPed$parameter )

  has_sample <- "sample_id" %in% colnames(ped)
  has_other  <- "other"     %in% colnames(ped)

if (has_sample || has_other) {

  if (has_sample) {
    id_cols <- "sample_id"
    if (!"sample_id" %in% colnames(predictions_wide)) {
      colnames(predictions_wide)[1] <- "sample_id"
    }
    if (has_other) {
      F1_ind <- ped[ped$crossType == "F1",
                    c("sample_id", "other", "designation")]
    } else {
      F1_ind <- ped[ped$crossType == "F1",
                    c("sample_id", "designation")]
    }
  } else {  # only "other" present
    id_cols <- "designation"
    F1_ind <- ped[ped$crossType == "F1",
                  c("other", "designation")]
  }

  # merge by the chosen ID column
  predictions_wide <- merge(predictions_wide, F1_ind, by = id_cols)

  OutputCols <- c(
    if (has_sample) "sample_id" else NULL,
    if (has_other) "other" else NULL,
    "designation",
    "mother","father","status","parental_uncertainty","probMatch",
    "heteroMexp","heteroMp","heteroDeviation",
    "avgScore","nScore2","nMarkers",
    "HasGeno","HasPed","parHetFilter","ParentHasGeno"
  )

  # avoid duplicates and keep only existing columns
  OutputCols <- unique(OutputCols)
  OutputCols <- intersect(OutputCols, colnames(predictions_wide))

  predictions_wide <- predictions_wide[, OutputCols, drop = FALSE]
}
  
  if("params" %in% ls()){ # we will download the document
    printTable(predictions_wide, autoWidthOpt = TRUE, scrollXOpt = FALSE,
             colNames = colnames(predictions_wide),
           numericColNames = numericalColumns,
           numRound = 3)%>%
  DT::formatStyle(
    'status',
    target = 'row',
    backgroundColor = DT::styleEqual(
      c('GOOD','QUESTIONABLE','UNCERTAIN',"BAD","PARENT FAIL"),
      c(
          "rgba(164, 214, 94, 0.3)",
          "rgba(192,202, 51, 0.22)",
          "rgba(255,209,102, 0.28)",
          "rgba(243,176,176, 0.30)",
          "rgba(215, 48, 39, 0.30)"
        )  
    )
  )
  }else{
    DT::renderDT({
  base_cols <- OutputCols[
    OutputCols %in% c("sample_id", "other", "designation",
                    "mother", "father", "status", "parental_uncertainty")
    ]
  
  cols <- c(base_cols, input$traitQa) 

  # Apply parental uncertainty filter
  display_data <- predictions_wide
  if (!is.null(input$filterUncertaintyPlot) && length(input$filterUncertaintyPlot) > 0 &&
      "parental_uncertainty" %in% colnames(display_data)) {
    display_data <- display_data[display_data$parental_uncertainty %in% input$filterUncertaintyPlot, , drop = FALSE]
  }

  tbl <- printTable(
    display_data[, cols, drop = FALSE],
    autoWidthOpt = FALSE,
    scrollXOpt   = TRUE,
    colNames     = cols,
    numericColNames = intersect(input$traitQa, cols),
    numRound     = 3
  ) %>%
    DT::formatStyle(
      "status",
      target = "row",
      backgroundColor = DT::styleEqual(
        c("GOOD","QUESTIONABLE","UNCERTAIN","BAD","PARENT FAIL"),
        c(
          "rgba(164, 214, 94, 0.3)",
          "rgba(192,202, 51, 0.22)",
          "rgba(255,209,102, 0.28)",
          "rgba(243,176,176, 0.30)",
          "rgba(215, 48, 39, 0.30)"
        )  
      )
    )

  tbl
}, server = FALSE)
  }
  
}

```

### Parental check
<p>&nbsp;</p>

The following plot shows how many F1 individuals derived from each parent received a "GOOD" status or failed. Parents that resulted in mostly failed F1s are more likely to have genotyping errors


```{r, out.width="100%"}

if (is.null(result)){
invisible(NULL)
} else {
.build_parent_data <- function(df, max_parents = 30) {
  # Stack mothers and fathers into a single "parent" column
  parent_long <- rbind(
    data.frame(parent = df$mother, status = df$status, stringsAsFactors = FALSE),
    data.frame(parent = df$father, status = df$status, stringsAsFactors = FALSE)
  )

  # Drop missing/empty parents
  parent_long <- parent_long[!is.na(parent_long$parent) & parent_long$parent != "", ]

  # Define outcome label
  parent_long$Outcome <- ifelse(
    parent_long$status == "GOOD",
    "Crosses passed QA",
    "Crosses failed QA"
  )

  # Count F1s per parent x outcome
  counts <- with(parent_long, as.data.frame(table(parent, Outcome)))
  colnames(counts)[3] <- "n"

  # Order parents by total number of F1s (descending)
  totals <- tapply(counts$n, counts$parent, sum)
  ordered_parents <- names(sort(totals, decreasing = TRUE))

  # Limit to top N parents for readability
  if (length(ordered_parents) > max_parents) {
    ordered_parents <- ordered_parents[1:max_parents]
    counts <- counts[counts$parent %in% ordered_parents, ]
  }

  counts$parent <- factor(counts$parent, levels = rev(ordered_parents))
  list(counts = counts, n_parents = length(ordered_parents))
}

dat <- .build_parent_data(predictions_wide)

if("params" %in% ls()){ # static HTML download — use ggplot (respects fig dimensions)
  # Compute figure height in inches: ~0.3 inches per parent, minimum 4 inches
  fig_h <- max(4, dat$n_parents * 0.3)
  knitr::opts_current$set(fig.height = fig_h)

  p <- ggplot2::ggplot(dat$counts, ggplot2::aes(x = n, y = parent, fill = Outcome)) +
    ggplot2::geom_col(position = "dodge") +
    ggplot2::scale_fill_manual(
      name = "QA result",
      values = c("Crosses passed QA" = "#6baed6", "Crosses failed QA" = "#fc9272")
    ) +
    ggplot2::labs(x = "Number of F1s", y = NULL) +
    ggplot2::theme_minimal() +
    ggplot2::theme(axis.text.y = ggplot2::element_text(size = 9, hjust = 1))

  print(p)

} else { # interactive Shiny rendering
  plot_h <- max(350, dat$n_parents * 25)
  p <- ggplot2::ggplot(dat$counts, ggplot2::aes(x = n, y = parent, fill = Outcome)) +
    ggplot2::geom_col(position = "dodge") +
    ggplot2::scale_fill_manual(
      name = "QA result",
      values = c("Crosses passed QA" = "#6baed6", "Crosses failed QA" = "#fc9272")
    ) +
    ggplot2::labs(x = "Number of F1s", y = NULL) +
    ggplot2::theme_minimal() +
    ggplot2::theme(axis.text.y = ggplot2::element_text(size = 9, hjust = 1))
  fig <- plotly::ggplotly(p, height = plot_h, tooltip = "all")
  htmltools::div(style = paste0("width:100%; height:", plot_h + 50, "px; overflow:visible; position:relative; margin-bottom:30px;"), fig)
}

}

```

#### Parental heterozygosity summary

The following table lists each parent, its observed heterozygosity (%), and whether it passed or failed the heterozygosity filter.

```{r}

if (is.null(result)){
  invisible(NULL)
} else {

  # Retrieve het threshold from modeling parameters
  het_thresh <- as.numeric(modeling[modeling$parameter == "ParentMaxHetThresh", "value"])

  # Build parent-level het info from predictions
  # parHetFilter is stored per F1, but het % must be computed from genotype data
  # We recompute per-parent heterozygosity from the marker matrix

  dtVerif <- result
  analysisIdForGeno <- modeling[modeling$parameter == "analysisId", "value"]

  if (inherits(dtVerif$data$geno, "genlight")) {
    qas <- which(names(dtVerif$data$geno_imp) == analysisIdForGeno)
    if (length(qas) > 0) {
      gl_obj <- dtVerif$data$geno_imp[[qas]]
      Markers_all <- as.data.frame(gl_obj)
      rownames(Markers_all) <- adegenet::indNames(gl_obj)
    }
  }

  ploidy_val <- as.numeric(
    dtVerif$metadata$geno[dtVerif$metadata$geno$parameter == "ploidity", "value"]
  )

  # Get unique parent IDs
  parent_ids <- unique(na.omit(c(predictions_wide$mother, predictions_wide$father)))
  present_parents <- intersect(parent_ids, rownames(Markers_all))

  if (length(present_parents) > 0) {
    M_par <- Markers_all[present_parents, , drop = FALSE]
    homo_mat <- (M_par == 0 | M_par == ploidy_val)
    n_non_missing <- rowSums(!is.na(M_par))
    n_homo <- rowSums(homo_mat, na.rm = TRUE)
    het_pct <- (pmax(n_non_missing - n_homo, 0) / pmax(n_non_missing, 1)) * 100

    par_het_df <- data.frame(
      Parent = present_parents,
      Heterozygosity_pct = round(het_pct, 2),
      Filter_Status = ifelse(het_pct <= het_thresh, "PASS", "FAIL"),
      stringsAsFactors = FALSE
    )

    # Add parents without genotype data
    missing_parents <- setdiff(parent_ids, present_parents)
    if (length(missing_parents) > 0) {
      par_het_df <- rbind(par_het_df, data.frame(
        Parent = missing_parents,
        Heterozygosity_pct = NA_real_,
        Filter_Status = "NO GENO DATA",
        stringsAsFactors = FALSE
      ))
    }

    # Sort: FAIL first, then by het descending
    par_het_df <- par_het_df[order(
      factor(par_het_df$Filter_Status, levels = c("FAIL", "NO GENO DATA", "PASS")),
      -par_het_df$Heterozygosity_pct
    ), ]
    rownames(par_het_df) <- NULL

    tbl <- printTable(
      par_het_df,
      autoWidthOpt = TRUE,
      scrollXOpt = FALSE,
      colNames = c("Parent", "Heterozygosity (%)", "Filter Status"),
      numericColNames = "Heterozygosity_pct",
      numRound = 2
    ) %>%
      DT::formatStyle(
        "Filter_Status",
        target = "row",
        backgroundColor = DT::styleEqual(
          c("PASS", "FAIL", "NO GENO DATA"),
          c("rgba(164, 214, 94, 0.3)", "rgba(215, 48, 39, 0.30)", "rgba(243,176,176, 0.30)")
        )
      )

    if ("params" %in% ls()) {
      tbl
    } else {
      DT::renderDT(tbl, server = FALSE)
    }
  }
}

```

### Verification Metrics

The following table shows summary metrics of the F1 (QA/QC analysis)

```{r, results='asis'}
if (is.null(result)){
  # invisible(NULL)
} else {
  numericalColumns2 <- c("value") 
  metricsVeri <- result$metrics[which( result$metrics$analysisId == idQa),]
  
  if("params" %in% ls()){ # we will download the document
    printTable(metricsVeri, autoWidthOpt = TRUE, scrollXOpt = FALSE,
             colNames = colnames(metricsVeri),
           numericColNames = numericalColumns2,
           numRound = 4)
  }else{
    DT::renderDT(printTable(metricsVeri,
                        autoWidthOpt = FALSE, scrollXOpt = TRUE,
                        colNames = colnames(metricsVeri),
                        numericColNames = numericalColumns2,
                        numRound = 4), server = FALSE)
  }
  
}

```

<p>&nbsp;</p>

### Verification Modeling

The following table shows the input parameters of the F1 (QA/QC analysis)

```{r, results='asis'}
if (is.null(result)){
  # invisible(NULL)
} else {
  # numericalColumns2 <- c("value") 
  modelingVeri <- result$modeling[which( result$modeling$analysisId == idQa),]
  
  if("params" %in% ls()){ # we will download the document
    printTable(modelingVeri, autoWidthOpt = TRUE, scrollXOpt = FALSE,
             colNames = colnames(modelingVeri))
  }else{
    DT::renderDT(printTable(modelingVeri,
                        autoWidthOpt = FALSE, scrollXOpt = TRUE,
                        colNames = colnames(modelingVeri)), server = FALSE)
  }
  
}

```
<p>&nbsp;</p>

### References on methods used

Tukey, J. W. (1977). Exploratory Data Analysis. Section 2C.

Velleman, P. F. and Hoaglin, D. C. (1981). Applications, Basics and Computing of Exploratory Data Analysis. Duxbury Press.


<p>&nbsp;</p>



